---
title: "Reproducible research assignment 1"
author: "Michal Ch"
output: html_document
---
##Loading and preprocessing the data

```{r}
echo = TRUE
library(knitr)
library(ggplot2)

activity_raw<-read.csv("activity.csv")
activity<-activity_raw
activity$date<-as.Date(activity$date,format="%Y-%m-%d")
activity_complete<-activity[complete.cases(activity),]
sum_per_day<-aggregate(steps ~ date, activity_complete, sum)
```



Plotting histogram with mean
```{r}
ggplot(
        data=sum_per_day, aes(sum_per_day$steps)) +
        geom_histogram(breaks=seq(0,20000, by=1000)) +
        labs(title="Frequency of days, by step count") +
        labs(x="Sum of steps per day",y="number of days") +
        geom_vline(aes(xintercept=mean(sum_per_day$steps)),color="red", linetype="dashed")
```  

##What is mean total number of steps taken per day?
```{r}
        mean<-mean(sum_per_day$steps)
        print(mean)
```
Median is
```{r}
        median<-median(sum_per_day$steps) 
        print(median)
```
        
##What is the average daily activity pattern?
```{r}
#aggregate failed, switching to data.table        steps_interval<-aggregate(steps ~ interval, activity_complete, mean)
        library(data.table)
        activity_complete2<-data.table(activity_complete)
#avarage activity per interval
        av_a<-activity_complete2[,mean(steps),by=interval]
            ggplot(av_a,aes(x=interval,y=V1))+
                       geom_line()+
                        labs(x="interval",y="avarage number of steps")+
                        labs(title="Avarage number of steps per interval")
```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
        maxi<-av_a[,which.max(V1)]
        av_a$interval[maxi]
        
```

##Imputing missing values

Number of rows with missing values
```{r}
        sum(!complete.cases(activity))
```

Filling them with avarage for that interval
```{r}
        activity_filled<-activity
        
```
##Are there differences in activity patterns between weekdays and weekends?


